There is one fact that keeps driving me towards believing in a higher power: wherever I went, I have always been surrounded and helped by many good people. My experience at graduate school is no exception.

My advisor, Prof. Aharon Kapitulnik, has inspired me, and will continue to inspire, not only with his knowledge and dedication, but also with almost Beethovenian passion and sincerity, both for science and for life, that I did not think was possible to be possessed by a person in real life, let alone someone outside the artistic professions.

Aharon is a member of the professorial tripartite that, according to legend, was introduced to Mikhail Gorbachev during his visit as the ``KGB of the West''. The other members, Theodore (Ted) Geballe and Malcolm (Mac) Beasley, being more senior, became emeriti prior to or during my time here. They have continued their dedication to science, as well as fostering us the new generations. Thanks to them, we have had glimpses into the arts of humor, diplomacy, and competent leadership. I hope that one day, if good fortunes continue to favor me, I may find in myself traces of the wisdom that is emanated continuously from Aharon, Ted, and Mac.

I was incredibly lucky to be supervised and mentored by Dr. Merav Dolev when I first arrived. She is a brilliant scientist, and an even better teacher. Every time I have mentored younger students myself since then, I was reminded of her by my own conscience: have I done my best for them to emulate what she for me; will I ever live up to her example?

The students, postdocs, and members of research staff in the KGB group have been the most helpful through out my time here. They are not only excellent collaborators in research, but also wonderful companions to develop an intellectual maturity with. If one day I will eventually acquire what Oscar Wilde would call the ``Oxford temper'', and become someone who is capable of playing gracefully with ideas, it would be, in no small part, thanks to the numerous discussions and debates that my colleagues indulged me with.

I would also like to thank my collaborators outside the KGB group, particularly, Prof. Alexander (Alik) Palevski at Tel Aviv University, Prof. Ian Fisher and his student, now Prof. Jiun-Haw Chu. The skills and knowledge I learned from them will undoubtedly continue to benefit me through out my career. 

\paragraph{}
I could not have completed this thesis without the support of my family. Grandpas and grandmas survived wars and famines that my generation could only imagine: yet they never showed any resentment or nihilism. Instead, they showered us with love, and set great examples of family values and personal responsibilities for us to follow. My parents overcame serious obstacles, and, through their hard work, provided me the best possible education. Without their labor, it would not be possible for me to partake in a scholarly profession, that was undoubtedly considered unworldly by previous generations. Aunt Jiqing and Uncle Jun gave me some of my best childhood memories, and introduced me to something called a computer, which turned out to be rather indispensable later on. Finally, Cousin Fang and Cousin Wenxin, who each overlapped with me for two years in Cambridge, England, allowing me to read my undergraduate course two continents away from home without spending a day not being loved by a sister down the street.

I am forever grateful to all the good people whom I have been blessed to befriend with. These include, but are by no means limited to, the Schulze family, whose friendship showed me that ``Alle Menschen werden Br\"uder'' is not merely a wishful dream of Schiller; Mr. Ian Craig, Mrs. Marion Meutzelfeldt, the Reverend Mr. Nicholas Blair, and all the wonderful members of staff at Merchiston Castle School; Dr. Malte Grosche, Prof. Philipp Gegenwart, and Dr. Yoshifumi Tokiwa, for their former guidance; Dr. Xixuan Wu and Dr. Shuai Shao, who brought a bit of my hometown to the Bay Area; and finally, Ms. Elisabeth Seaman, whose kindness and generosity would rekindle in the most stubborn pessimist a faith in humanity.

\paragraph{}
Part of the data presented in this thesis is resulted from collaborated experiments. The pulsed laser deposition (PLD) recipe for Bi$_2$Se$_3$ thin films was developed together with Li Zhang. The PLD targets for EuS and Bi$_2$Se$_3$ were fabricated at the University of California, Davis, by Jinfeng Zhao and Subhash H. Risbud. Polar Kerr effect measurements by Sagnac interferometry were performed and analyzed by Elizabeth Schemm and Alexander Fried. Transmission electron microscopy was performed by Ann F. Marshall as part of a training demonstration.

Sample characterization was partly performed at the Stanford Nano Shared Facilities (SNSF), supported by the National Science Foundation under award ECCS-1542152.  This work is supported by the Department of Energy,  Office of Science, Basic Energy Sciences, Materials Sciences and Engineering Division, under Contract DE-AC02-76SF00515. Initial work was supported by DARPA, MesoDynamic Architecture Program (MESO) through the contract number N66001-11-1-4105.